---
title: "Tidy Tuesday 4"
description: |
  Which vegetables got cumulatived the most?
author: []
date: 09-11-2022
output:
  html_document:
    df_print: paged
    code_download: true
    theme: cerulean
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```

Load the library: 

```{r}
library(dplyr)
library(ggplot2)
library(gghighlight)
library(googlesheets4)
library(lubridate)
```

Here is the dataset: 

```{r}


gs4_deauth() #To not have to authorize each time you knit.

harvest_2021 <- read_sheet("https://docs.google.com/spreadsheets/d/1DU6dpxrbPGW2oJHQ6TG_xibazoGhvmRcqk2iPGOaRUI/edit?usp=sharing") %>%
mutate(date = ymd(date))
```

```{r}
harvest_2021
```

Looking at the dataset, for this week's tidy tuesday, I am planning to find the top 3 vegetables with the highest cumulative weight after a period of time. 

First, I will try to explore the min and the max date for the plot: 

```{r}
harvest_2021 %>% 
  summarise(min(date), max(date))
```

After that, I will plot the graph to see which vegetables have the highest weight cumulative overall: 

```{r}
harvest_2021 %>% 
  mutate(wt_lbs = weight*0.00220462) %>% 
  group_by(vegetable, date) %>%
  summarize(daily_wt_lbs = sum(wt_lbs)) %>% 
  mutate(cum_wt_lbs = cumsum(daily_wt_lbs)) %>% 
  arrange(cum_wt_lbs) %>% 
  ggplot(aes(x = date, y = cum_wt_lbs, color = vegetable)) +
  geom_line() + 
  gghighlight(max(cum_wt_lbs) > 90) + 
  labs(title = "The vegatable's cumulative weight in pounds from May 2021 to October 2021",
       y = "",
       x = "") + 
  theme_minimal() + 
  theme(# remove the vertical grid lines
        panel.grid.major.x = element_blank() ,
        panel.grid.major.y = element_line( size=.05, color="black")) 
```

We can clearly see that tomatoes, pumpkin and squash have the 3 highest cumulative weight overall. 




