---
title: "First Tidy Tuesday 09/08/2021"
description: |
  Here is my first tidy tuesday. It will improve over time!
author:
  - name: DucNgo
    url: {}
date: 09-09-2021
output:
  distill::distill_article:
    self_contained: false
---

```{r}
library(tidyverse)         # for graphing and data cleaning
```


```{r}
# Get the Data
constructors <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-07/constructors.csv')
constructor_standings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-09-07/constructor_standings.csv')

```

```{r}
constructor_standings %>%
  group_by(constructorId) %>%
  summarize(total_points = sum(points)) %>%
  filter(constructorId < 50) %>%
  ggplot(aes(x = constructorId, y = total_points)) + geom_col(fill = "blue") + 
  labs(title = "The total number of points for the first 50 constructors")
```

For this week's data, I decide to look into the constructor ID and the total number of points for the first 50 constructors. We can see that constructor number 6 - ferrari has the highest points of them all. 

Right now, the question I have is that when I try to filter the top constructor and I try to make a geom_col, the graph is not looking great. The reason for that is because we have a lot of constructors and when I filter it, the constructor is really far apart. So how can I do it? 

Moreover, I would love to know the name of the constructors. Is there any way to combine constructor_standings with constructors? I have tried full join but it does not look great. 


